\section[Section]{Objectives}

\begin{frame}
\frametitle{Objectives}
\begin{itemize}
    \item Understand how Git works and how to apply that to day to day
          development
    \item Learn the basic 12 everyday commands
    \item Know how to undo mistakes
    \item Learn how to use Git to collaborate
    \item Learn how to find help
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{12 Everyday Commands}
\begin{multicols}{3}
    \begin{itemize}
        \setlength\itemsep{3em}
        \item add
        \item branch
        \item checkout
        \item commit
        \item diff
        \item fetch
        \item help
        \item log
        \item merge
        \item push
        \item rebase
        \item status
    \end{itemize}
\end{multicols}
\end{frame}
\note[itemize]{
    \item Git has 160 subcommands in 2.9.3
    \item I'll cover about 20 of them
    \item These are the 12 you'll use daily
}

\begin{frame}
\frametitle{Finding Help}
\alert{Demo 01}: \texttt{git help}
\end{frame}
\note[itemize]{
    \item I'll cover one of them right now.
    \item Demo 01: git help
}

\begin{frame}
\frametitle{12 Everyday Commands}
\begin{multicols}{3}
    \begin{itemize}
        \setlength\itemsep{3em}
        \item add
        \item branch
        \item checkout
        \item commit
        \item diff
        \item fetch
        \item \alert{help}
        \item log
        \item merge
        \item push
        \item rebase
        \item status
    \end{itemize}
\end{multicols}
\end{frame}
\note[itemize]{
    \item One down, 11 to go.
}

\begin{frame}
\frametitle{Learn 4 Ways}
\begin{itemize}
    \setlength\itemsep{3em}
    \item Conceptual
    \item Commands
    \item Implementation
    \item Try It
\end{itemize}
\end{frame}
\note[itemize]{
    \item Conceptual - Computer science lecture. Diagrams of directed acyclic
          graphs and reachability. I'll lecture. We'll watch some lectures from
          Scott Chacon (Author of "Pro Git", CIO GitHub).
    \item Commands - Practical. How to use common commands.
    \item Implementation - How Git works under the hood.
    \item Try It - Practice!
}
